Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-14 paper/paper.tex
pass on Section IV

The first criterion focuses on actively maintained projects whereas
the second criterion focuses on popular cases. As we wanted to report
bugs, we also looked for project with public issue trackers.
Table~\ref{tab:engines} shows the engines we selected in this
study. We made an exception to the second criterion with
XS~\Fix{cite}. As the project is young, created in Oct 2017, we
thought there was insufficient time to obtain 1K stars for XS. We
still considered this project as it seems to be attracting interest
from the community\Fix{is this true?}
\Igor{eu pensei sobre isso, acho que nao eh relevante colocar o XS sendo 
que ele eh uma engine para iot/embarcados, temos como exemplo o 
JerryScript que tambem tem o mesmo proposito e esta ha bem mais tempo
que ele. Por mim, utilizamos apenas o Jerry ou os dois (e compara-los ja que 
sao similares), oq vc acha?}. It is worth noting that we used
JSVU~\cite{jsvu} to automatically install and configure versions of
different JS engines in our host environment. This is important as we
aim to use the most recent stable versions of each engine as to avoid
reporting old and already-fixed bugs to developers.

\begin{table}[t]
  \centering
  \caption{\label{tab:engines}Engines Analyzed}
  \begin{tabular}{cccr}
    \toprule
    Group & Name & URL & \# Stars \\
    \midrule
    Apple & JavaScriptCore (WebKit) & \cite{jsc2018repo} & \multicolumn{1}{c}{-} \\
    Google & v8 & \cite{v82018repo} & 9800+ \\
    JerryScript & JerryScript & \cite{jerryscript2018repo} & 3100+ \\
    Microsoft & Chakra & \cite{chakra2018repo} & 7200+ \\
    Moddable & XS & \cite{xs2018repo} & 140+ \\
    \midrule
    \multirow{2}{*}{Mozilla} & Rhino & \cite{rhino2018repo} & 1800+ \\
    & SpiderMonkey & \cite{spidermonkey2018repo} & \multicolumn{1}{c}{-} \\
   \bottomrule     
  \end{tabular}
\end{table}

\subsection{Seed JS files\label{sec:seeds}}~
We selected test files from several public projects from GitHub. We
looked for self-contained tests from JS engine projects, initially
using the GitHub REST API\Fix{cite}. We noticed that some of the tests
we found depend on external libraries, which not all engines we use
(see Section~\ref{sec:methodology:engines}) support. We decided to
discard those. For example, many tests we found required a
nodejs\Fix{cite} runtime for execution. Overall, we considered the
test suites of three of the four engines mentioned in
Section~\ref{sec:methodology:engines} and four other engines.
Table~\ref{tab:test-suites} shows the JS sources we considered for
each of the selected projects. Overall, we found a total of
\totfiles{} JS files. It is worth noting that some projects use
distinct frameworks for testing and require external libraries to run
their testing suites. 
For these projects, we needed to make small
changes in the testing infrastructure to be able to uniformly run
tests in all engines. For example, some of the files does not use assertion 
functions defined in their projects; we replaced those with our definitions.
\Mar{not sure if this
  is a good example; why one would like to redefine assertion? why
  didn't you incorporate the assertion function to your infra?}
\Igor{sim, poderiamos fazer isso. Porem, lembro que alguns testcases por exemplo usam 
algo diferente de "assert", outras usam alguma funcao interna 
que apenas uma engine suporta. Eu posso analisar melhor aqui nossas seeds 
e ver um jeito global de resolver isso, como se fosse um "shell.js" da nossa 
ferramenta.}

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Test Suites
  % \Mar{try to use a single
  %     name (if possible) to facilitate reference in the paper. Use the
  % full path in the URL (citation) to indicate where one can find those
  % files.}
  }
  \begin{tabular}{ccr}
    \toprule
    Name & Source & \# JS files \\
    \midrule
    Mozilla & \cite{mozilla} & 32,414 \\
    V8 & \cite{v8} & 64 \\
    WebKit & \cite{webkit} & 1,031 \\
    \midrule    
    Duktape & \cite{duktape} & 997 \\
    JerryScript & \cite{jerryscript} & 1,803 \\
    JSI & \cite{jsi} & 99 \\
    Tiny-js & \cite{tinyjs} & 44 \\    
    % Chakra & \cite{chakracore} & 2632 \\
    \midrule
     &  & 36,452 \\
   \bottomrule     
  \end{tabular}
\end{table}

>>>>

We look for highly-maintained (as per the first criterion) and popular
(as per the second criterion) projects. As we wanted to report bugs,
we also looked for project with public issue trackers.
It is worth noting that we used
GoogleChromeLab's JSVU~\cite{jsvu} to automatically install and configure versions of
different JS engines in our host environment. This is important as we
aim to use the most recent stable versions of each engine as to avoid
reporting old and already-fixed bugs to developers.

%% Table~\ref{tab:engines} shows the engines we selected in this
%% study. We made an exception to the second criterion with
%% XS~\cite{xs2018repo}. As the project is young, created in Oct 2017, we
%% thought there was insufficient time to obtain 1K stars for XS. We
%% still considered this project as it seems to be attracting interest
%% from the community\Fix{is this true?}

\begin{table}[t]
  \centering
  \caption{\label{tab:engines}Engines Analyzed.}
  \begin{tabular}{cccr}
    \toprule
    Group & Name & URL & \# Stars \\
    \midrule
    Apple & JavaScriptCore (WebKit) & \cite{jsc2018repo} & \multicolumn{1}{c}{-} \\
    Google & v8 & \cite{v82018repo} & 9800+ \\
    JerryScript & JerryScript & \cite{jerryscript2018repo} & 3100+ \\
    Microsoft & Chakra & \cite{chakra2018repo} & 7200+ \\
%    Moddable & XS & \cite{xs2018repo} & 140+ \\
    \midrule
    \multirow{2}{*}{Mozilla} & Rhino & \cite{rhino2018repo} & 1800+ \\
    & SpiderMonkey & \cite{spidermonkey2018repo} & \multicolumn{1}{c}{-} \\
   \bottomrule     
  \end{tabular}
\end{table}

\subsection{Seed JS files\label{sec:seeds}}~
We selected test files from several public projects from GitHub. We
looked for self-contained tests from JS engine projects, initially
using the GitHub REST API~\cite{github-rest-api}. We noticed that some
of the tests we found depend on external libraries, which not all
engines we use (see Section~\ref{sec:methodology:engines}) support. We
decided to discard those. For example, many tests we found required a
Node.js runtime~\cite{node} for execution. We considered the offical
TC-39~\cite{tc39-github} conformance test suite for the ECMA262
specification~\cite{ecmas262-spec}. Furthermore, we considered test
suites of three of the four engines mentioned in
Section~\ref{sec:methodology:engines} and four other engines.
Table~\ref{tab:test-suites} shows the JS sources we considered for
each of the selected projects. Overall, we found a total of
\totfiles{} JS files. It is worth noting that some test suites use
distinct frameworks for testing and require external libraries to run
their testing suites.  For these projects, we needed to make small
changes in the testing infrastructure to be able to run the tests
uniformly across all engines. More precisely, we needed to mock
functions, related to the test harness, which are only available to
certain engines.

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Test Suites. The sections of the
    table show, respectively, the TC-39 conformance test suite, suites
    from engines we analyzed, and other suites.}
  \begin{tabular}{ccr}
    \toprule
    Name & Source & \# JS files \\
    \midrule
    TS-39 & \cite{ecma262-conformance-suite} & \Fix{-} \\
    \midrule
    Mozilla & \cite{mozilla} & 32,414 \\
    V8 & \cite{v8} & 64 \\
    WebKit & \cite{webkit} & 1,031 \\
    \midrule    
    Duktape & \cite{duktape} & 997 \\
    JerryScript & \cite{jerryscript} & 1,803 \\
    JSI & \cite{jsi} & 99 \\
    Tiny-js & \cite{tinyjs} & 44 \\    
    % Chakra & \cite{chakracore} & 2632 \\
    \midrule
     &  & 36,452 \\
   \bottomrule     
  \end{tabular}
\end{table}
